\vfill A Testing Framework for Web Application

### 2014-01-31 Paper/paper.tex
PDF added, better organization, partial entry for RW

I also found research into common bugs, general testing techniques, and finding bugs that greatly improved my test cases.

@@

\cite{FrameworkForAutomatedTesting}

\cite{MultiAgentSoftwareEnvironment}

\cite{2LayerModel}

\cite{InvariantBasedUseInterfaces}

\cite{JSART}

\cite{DOMTransactions}

\cite{TestingInPractice}

\cite{ContractDrivenTesting}

\cite{JAWS}

\cite{WebMate}

\cite{BookContinuousTesting}

\subsection{Finding Bugs}
\cite{FindingBugs}

\cite{TestingWebServicesSurvey}

\cite{RESTfulFramework}

\subsection{Writing Effective Test Cases}
\cite{GoingFaster}

>>>>

I also found research into common bugs, general testing techniques, and finding bugs that greatly improved my test cases and understanding.

@@

\subsubsection{``A Framework for Automated Testing of JavaScript Web Applications'' \cite{FrameworkForAutomatedTesting}}
A collection of IBM Researchers and two university students came up with a framework called ``Artemis'' for testing web applications. What is novel about their tool is that it generates test cases automatically based on execution patterns and feedback. They have attempted to solve the problem that writing test cases by hand is both time-consuming and often difficult. Their automatic test generation lead to an average of 69\% test coverage with enough tests generated.

Though it was an interesting and somewhat effective method, 69\% coverage is not great and this particular framework only covers the client-side, so it was incomplete for our purposes.

\subsubsection{\cite{MultiAgentSoftwareEnvironment}}

\subsubsection{\cite{2LayerModel}}

\subsubsection{\cite{InvariantBasedUseInterfaces}}

\subsubsection{\cite{JSART}}

\subsubsection{\cite{DOMTransactions}}

\subsubsection{\cite{TestingInPractice}}

\subsubsection{\cite{ContractDrivenTesting}}

\subsubsection{\cite{JAWS}}

\subsubsection{\cite{WebMate}}

\subsubsection{\cite{BookContinuousTesting}}

\subsection{Finding Bugs}
\subsubsection{\cite{FindingBugs}}

\subsubsection{\cite{TestingWebServicesSurvey}}

\subsubsection{\cite{RESTfulFramework}}

\subsection{Writing Effective Test Cases}
\subsubsection{\cite{GoingFaster}}
